\begin{abstract}
The usage and integration of radar technologies for the implementation of odometry has recently emerged as a promising alternative to traditional methods, which often rely on visual or LiDAR-based systems.
This integration can also improve existing approaches for odometry estimation such as wheel encoders, inertial measurement units (IMUs), and GPS-based positioning.

\begin{comment}
    [25/09/2025]
    This section needs to be improve to go into the point.
\end{comment}
This work focus in the estimation of the vehicle's ego-motion using a dual mmWave radar sensor system and an inertial motion sensor.
Related work, including radar-only odometry and multimodal sensor fusion, is discussed to contextualize the contributions of this research within the broader field of autonomous vehicle navigation.

The proposed pipeline incorporates clustering techniques, point-to-point iterative closest point (ICP) optimization, and Doppler velocity augmentation to address the inherent challenges of sparse and noisy radar point clouds.
Notably, the point-to-point ICP approach is advantageous for radar-based odometry as it does not require an initial guess of the transformation, which is often difficult to obtain due to data sparsity and noise.
Furthermore, submap aggregation is employed to enhance registration stability across consecutive scans. 
Experimental evaluations demonstrate that the proposed framework enables consistent ego-motion estimation and highlights the potential of mmWave radar as a cost-efficient solution for autonomous navigation and digital twin construction in complex driving environments.

\end{abstract}

\begin{IEEEkeywords}
Radar Odometry, mmWave Radar, ICP, Doppler Velocity, Doppler Augmentation, Ego-Motion Estimation
\end{IEEEkeywords}

