\section{Objective and Sub-Tasks}
\label{sec:objective}
The main objective of this work is the development of a radar-based odometry system that estimates the vehicle ego-mmotion using mmWave radar sensors mounted at the fron of the vehicle.
That motivation behind this approach is to explore radar as a cost-effective and robust alternative to the existing solutions based in vision or LiDAR-based odometry, particularly in conditions where those have the tendency to fail.

The system processes radar point cloud data enriched with range, angle and the most important of all, Doppler velocity, aiming to extract accurate motion for ego-velocity or speed estimation.
This to be able to recreate the trajectory of the vehicle and be able to use this information for SLAM applications.

\begin{figure}[!htbp]
    \centering
    \begin{tikzpicture}
        \gokart{0}{0}{0}
    
        % Wall (three cubes)
        \draw[fill=gray] (-0.6,3) rectangle (-0.2,3.4);
        \draw[fill=gray] (-0.2,3) rectangle (0.2,3.4);
        \draw[fill=gray] (0.2,3) rectangle (0.6,3.4);
    
        % Dashed line from go-kart to wall (center axis)
        \draw[dashed, thick] (0,-2) -- (0,3.5);
    
        % Range brace annotation
        \draw [decorate, decoration = {brace, raise=10pt}] (0.7,3) -- (0.7, 0) node[pos=0.5,right=10pt,black]{\SIrange{10}{11}{\meter}};

        % Enlarged Radar sensor boxes
        \draw[fill=blue!30] (-0.4,-0.3) rectangle (-0.2,-0.1);

        \draw[fill=blue!30] (0.2,-0.3) rectangle (0.4,-0.1);
    \end{tikzpicture}
    \caption{Test scenario with dual front-mounted mmWave radar sensors.}
    \label{fig:test_scenario}
\end{figure}

The experimental setup is illustrated in Figure \ref{fig:test_scenario}, where 2 mmWave radar sensors are mounted at the front of a vehicle, providing overlapping fields of view to enhance environmental perception.
The dual sensor congfiguration improves the spatial coverage, reducing the blind spots and providing a more dense amount of information about the environment for a more stable processing for odometry compared to a single sensor configuration.
Each sensor provides a point cloud with range, angle, and Doppler velocity information.
Both perspectives are processed by each sensor independently and then merge into a single point cloud for further processing.
Creating a more robust and reliable input for the odometry estimation pipeline, enabling the evaluation of radar-based odometry performance in realistic driving scenarios.


\subsection{Sub-Tasks}

The research objective, together with the constraints of using a dual-radar sensor, implied several practical sub-tasks:  
\begin{itemize}
    \item Designing a modular pipeline to acquire and decode synchronized radar data from both sensors.
    \item Investigating suitable sensor configurations to balance field of view, update rate, and data density.  
    \item Selecting sensor configurations that balance chirp bandwidth, update rate, and detection density.
    \item Applying RANSAC filtering on Doppler velocities to reject dynamic points and outliers.
    \item Implementing clustering methods to structure radar detections and isolate relevant features.  
    \item Integrating Doppler velocity information into the odometry estimation process.   
    \item Employing submap aggregation to mitigate sparsity and improve stability. 
    \item Performing ICP alignment between submaps aggregated from both sensors to mitigate sparsity and noise. 
    \item Evaluating the influence of the dual-sensor arrangement on odometry accuracy and robustness. 
    \item Validating the complete system on real-world driving scenarios. 
\end{itemize}

As each sub-task builds upon the results of the previous one, the work followed an iterative and modular development approach, enabling gradual integration and continuous evaluation of the proposed system.  