\newpage

\begin{thebibliography}{00}

\bibitem{ninebot_product_page} Segway Inc., ``Ninebot Go-kart PRO product page'', 2025, Webpage. [Online]. Available: \url{https://de-de.segway.com/products/ninebot-gokart-pro}

\bibitem{iwr_awr_diff} Texas Instruments, ``IWR1642: difference between AWR and IWR parts'', 2025, Webpage. [Online]. Available: \url{https://e2e.ti.com/support/sensors-group/sensors/f/sensors-forum/742730/iwr1642-difference-between-awr-and-iwr-parts}

\bibitem{dev_board_page} Texas Instruments, ``IWR6843AOPEVM product page'', 2025, Webpage. [Online]. Available: \url{https://www.ti.com/tool/IWR6843AOPEVM}

\bibitem{mmwave_demo_doc} Texas Instruments, ``User's Guide mmWave Demo Visualizer,'' 2020, Online Document. [Online]. Available: \url{https://www.ti.com/lit/ug/swru529c/swru529c.pdf?ts=1742817596204}.

\bibitem{mmwave_demo_web} 
Texas Instruments, 
``mmWave Demo Visualizer'', 2025, Webpage. [Online]. Available: \url{https://dev.ti.com/gallery/view/mmwave/mmWave_Demo_Visualizer/ver/3.6.0/}

\bibitem{understanding_uart} Texas Instruments, ``Understanding UART Data Output Format'', 2025, Webpage. [Online]. Available: \url{https://dev.ti.com/tirex/content/radar_toolbox_2_20_00_05/docs/software_guides/Understanding_UART_Data_Output_Format.html}

\bibitem{mmwave_demo_output} Texas Instruments, ``mmWave Sensing Estimator'', 2025, Webpage. [Online]. Available: \url{https://dev.ti.com/gallery/view/mmwave/mmWaveSensingEstimator/ver/2.5.1/}

\bibitem{ninebot_protocol_github} ub4raf, ``Ninebot-PROTOCOL'', 2025, GitHub Repository. [Online]. Available: \url{https://github.com/ub4raf/Ninebot-PROTOCOL}

\bibitem{ninebot_protocol_scooterhacking} -, ``Ninebot ES Communicaton Protocol'', 2019, Webpage. [Online]. Available: \url{https://cloud.scooterhacking.org/release/nbdoc.pdf}

\bibitem{numpy_polyfit} -, ``numpy.polyfit documentation'', 2025, Webpage. [Online]. Available: \url{https://numpy.org/doc/stable/reference/generated/numpy.polyfit.html}

\bibitem{OccupancyGrid_Mapping_Automotive} Ç. Önen, A. Pandharipande, G. Joseph, and N. J. Myers, ``Occupancy Grid Mapping for Automotive Driving Exploiting Clustered Sparsity,'' \textit{IEEE Sensors Journal}, vol. 24, no. 7, pp. 9240-9250, 2024. [Online]. Available: \url{https://doi.org/10.1109/JSEN.2023.3342463}.

\bibitem{Odometry_radar_only}
D. Casado Herraez, M. Zeller, L. Chang, I. Vizzo, M. Heidingsfeld, and C. Stachniss, 
``Radar-Only Odometry and Mapping for Autonomous Vehicles,'' 
\textit{arXiv preprint}, 2023. [Online]. Available: \url{https://arxiv.org/abs/2305.12409}

\bibitem{EgoMotion_DopplerRadar}
S. R. Bhatt, B. S. Nadiger, R. Parthasarathy, and H. M. Shetty, 
``Instantaneous Ego-motion Estimation Using Doppler Radar,'' 
\textit{IEEE Sensors Letters}, vol. 7, no. 5, pp. 1–4, 2023. [Online]. Available: \url{https://doi.org/10.1109/LSENS.2023.3244030}

\bibitem{Multimodal_Offroad}
C. E. Beal, T. Williams, J. Pauli, M. Mukadam, and B. Boots, 
``Robust Off-Road Autonomy Using Multimodal Sensor Fusion,'' 
in \textit{Proc. of the Conference on Robot Learning (CoRL)}, 2023. [Online]. Available: \url{https://openreview.net/forum?id=kmiZqSgoAt}

\bibitem{HighSpeed_Estimation}
B. Sundaralingam, C. E. Beal, and B. Boots, 
``Robust High-Speed State Estimation for Off-Road Autonomous Vehicles,'' 
in \textit{Proc. of Robotics: Science and Systems (RSS)}, 2023. [Online]. Available: \url{https://openreview.net/forum?id=3JpFLY3ihix}


\bibitem{geeksforgeeks_dbscan}
GeeksforGeeks, 
\emph{DBSCAN Clustering in ML | Density Based Clustering}, 
2023. [Online]. Available: \url{https://www.geeksforgeeks.org/dbscan-clustering-in-ml-density-based-clustering/}. [Accessed: 19-Mar-2025].

\bibitem{mathworks_kalman}
MathWorks,
\textit{Understanding Kalman Filters, Part 3: Optimal State Estimator},
2017. Available at: \url{https://la.mathworks.com/videos/understanding-kalman-filters-part-3-optimal-state-estimator--1490710645421.html} (Accessed: March 23, 2025).

\bibitem{ti_radar_toolbox}
Texas Instruments, 
\textit{Radar Toolbox – mmWave Sensor Configuration and Demos}, 
2024. Available at: \url{https://dev.ti.com/tirex/explore/node?node=A__ADnbI7zK9bSRgZqeAxprvQ__radar_toolbox__1AslXXD__2.20.00.05} (Accessed: March 23, 2025).

\bibitem{mti710_manual}  
Movella (Xsens),  
\textit{MTi User Manual},  
2023. [Online]. Available: \url{https://www.xsens.com/hubfs/Downloads/usermanual/MTi_usermanual.pdf}. [Accessed: 26-Sep-2025].  

\bibitem{xsens_repo}  
Scottapotamas,  
\textit{Xsens MTi Device Interface and Parser},  
GitHub repository, 2020. [Online]. Available: \url{https://github.com/Scottapotamas/xsens-mti}. [Accessed: 26-Sep-2025].  

\bibitem{mti_lowlevel_doc}  
Movella (Xsens),  
\textit{Low-Level Communication Protocol Documentation},  
2023. [Online]. Available: \url{https://www.xsens.com/hubfs/Downloads/Manuals/MT_Low-Level_Documentation.pdf}. [Accessed: 27-Sep-2025].  

\bibitem{googlemaps_fhdo}
Google Maps, 
\emph{Fachhochschule Dortmund - Parking Lot Overview}, 
2025. [Online]. Available: \href{https://www.google.com/maps/search/fh+dortmund/@51.5061964,7.4567,105m/data=!3m1!1e3?entry=ttu&g_ep=EgoyMDI1MDkyOC4wIKXMDSoASAFQAw%3D%3D}{Google Maps}. 
[Accessed: 01-Oct-2025].


\end{thebibliography}