\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{listings}
\lstset{breaklines=true}
\usepackage{url}
\usepackage{hyperref}
\usepackage{dirtree}
\graphicspath{ {images/} }
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{subcaption}
\usepackage{placeins}
\usepackage{comment}
\usetikzlibrary{positioning}
\usepackage{float}
\usepackage{tikz}
\usepackage{hyperref}
\usepackage{indentfirst}
\usetikzlibrary{calc, patterns, patterns.meta, shapes.geometric, arrows.meta, positioning, fit, decorations.pathreplacing, trees, arrows, shapes.misc, angles, quotes}
%Go-kart command \gokart{"x"}{"y"}{"rot_in_deg"}
\def\gokart#1#2#3{
    \begin{scope}[shift={(#1,#2)}, rotate=#3]
        \begin{scope}[shift={(0,-0.85)}] %Offset so (x,y) is the front bumper
            %Front bumper
            \draw[very thick] (-0.7, 0.75) -- (-0.5, 0.85) -- (0.5, 0.85) -- (0.7, 0.75);
            %Body
            \draw[fill=gray!30] (-0.5,-0.75) rectangle (0.5,0.75);
            %Wheels
            \draw[fill=black, rounded corners=0.75] (-0.6,0.6) rectangle (-0.4, 0.3); % Front left
            \draw[fill=black, rounded corners=0.75] (0.6,0.6) rectangle (0.4, 0.3); % Front right
            \draw[fill=black, rounded corners=0.75] (-0.6,-0.6) rectangle (-0.4, -0.3); % Rear left
            \draw[fill=black, rounded corners=0.75] (0.6,-0.6) rectangle (0.4, -0.3); % Rear right
            %Rear bumper
            \draw[very thick] (-0.6, -0.75) -- (-0.5, -0.8) -- (0.5, -0.8) -- (0.6, -0.75);
        \end{scope}
    \end{scope}
}

% Allow pseudo subsubsubsections
\newcommand{\subsubsubsection}[1]{\paragraph{#1}}

\usepackage{siunitx} 
\sisetup{locale = US}
\DeclareSIUnit{\Bit}{Bit}
\DeclareSIUnit{\baud}{Baud}
\DeclareSIUnit{\frame}{f}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\pagestyle{plain}

\begin{document}

\title{Radar odometry using mmWave technology for SLAM applications.\\
{\large Leveraging mmWave Radar Sensor Technology for odometry estimation.}
}

\author{\IEEEauthorblockN{Luis Fernando Rodriguez Gutierrez}
\IEEEauthorblockA{\textit{Fachhochschule Dortmund} \\
\textit{M.Eng. Embedded Systems Engineering}\\
luis.rodriguez001@stud.fh-dortmund.de}

}


\maketitle


\input{section/00abstract}
\input{section/01introduction}
\input{section/02SystemDesign}
\input{section/03SystemHardware}
\input{section/04MechanicalIntegration}
\input{section/05SensorSetupCalibration}
\input{section/06PipelineTransformation}
\input{section/07PipelineFrameAggregator}
\input{section/08PipelineFiltering}
\input{section/09PipelineRansac}
\input{section/10PipelineClustering}
\input{section/11PipelineClusterTracking}
\input{section/12PipelineICP}
\input{section/13Results}
\input{section/14Conclusion}

%\input{section/XX_WIP}
\input{Bibliography}


\end{document}

\begin{comment}
    [26/09/2025]
    [Guide Outline — Pre-thesis Structure]

    Abstract  
    - High-level summary: problem → method → key results → significance.  

    Introduction  
    - Background (odometry, current methods).  
    - Motivation (why radar odometry, why this project).  
        - General objective: main project goal.
    - Research gap (what existing methods lack).  
    - Contribution statement (what you did).
        - Without going into technical details.
        - Without doing into depth.

    SYSTEM DESIGN AND METHODOLOGY
        Research design
            - Explain the conceptual and mathematical framework.
            - Specific objectives: concrete steps
                - Design mounts (conceptual justification, not CAD details).
                - Configure chirps (parameters, mathematical rationale).
                - Implement filtering pipeline (mathematical description).
                    - Show pipeline diagram here (block diagram).

        System Hardware
            - Sensors (radar, IMU, webcam).
            - Mechanical integration (3D printed mounts, placement).
            - Sensor configuration
                - Radar setup.
                    - Sensor configuration.
                    - Sensor transformations.
                    - Chirp configuration.
                - IMU setup.
            * Keep at a descriptive/theoretical level (role of each hardware element in methodology). 

        Methodology (Pipeline)
            - Present the pipeline as the method.
            - Each subsection = one module (Transformations, Frame Aggregation, RANSAC, Clustering, ICP).
            - For each: explain mathematical approach, algorithm logic, expected effect.
            - Show diagrams (block flowcharts, data transformations).
            - End with summary of expected advantages of this design.

    Implementation & Experimental Setup (Showcasing your work)
        - Describe actual implementation process (code, synchronization, data collection).
        - Explain experimental platform (Ninebot test vehicle, dual radars, IMU, lab environment).
        - Show photos/screenshots (sensor mounts, test tracks, visualizations).
        - Here we describe *how it was realized in practice*, not the math.  

    Results & Discussion
    - Initial results (trajectory plots, ego-speed estimation, cluster visualization).  
    - Comparison with previous work (paper approach, wheel encoder, or naive ICP).  
        - Compare with full ICP vs cluster ICP.
    - Discuss successes and limitations.  

    Future Work  
    - Interpret results: where radar odometry shines, where it struggles.  
    - How your design choices (dual radars, chirp config, RANSAC filtering) affected performance.  

    Conclusion 
    - Wrap up contributions.  
    - Highlight possible extensions (sensor fusion, better clustering, real-world driving).  

    Bibliography  
\end{comment}
